Isomorphisms between algebraic datatypes

### 2025-08-14 QADT/notes.tex
QADT notes and open problems
new entry in QADT notes

\usepackage{amsmath}
\usepackage{amssymb}

@@

\begin{document}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}

@@

\newcommand{\hired}[1]{\textcolor{Red}{#1}}
\begin{document}

\section*{2025.08.14}

Looked at the equation $1 + X = X + X^2$.
Ben presented a method for deriving an ADT solution to this equation.
The following points came up during the discussion.
\begin{itemize}
  \item The answer matches up with the polynomial obtained by the trick
  $X := Z + 2$; this should be explained.
  \item Similarly, for any adt with roots $p$ and $-q$, we can
  write $F(x) = x + (x+1)(x+(q+p+1))$, then $\mu F + (p+1)$ gives those roots.
  \item Adding two \emph{linear} ADTs corresponds to adding their roots.
  \item How does the sum/product of two \emph{general} ADTs influence their
  roots?
  \item What is the general method for treating a ``difference'' of two
  ADTs $P(x) - Q(x)$, as an ADT in its own right?
  \item \hired{AP:} The trick of adding \emph{positive integers} to ADT
  seems to work for specific roots, specifically it should work for all real roots.

  How do we treat roots that have a complex component to them?
\end{itemize}

\section*{2025.07.22}
\begin{itemize}
  \item Theorem giving sufficient condition for surjectivity of the fold
  (from the initial algebra of a functor to any other fixed point of it)
  in terms of the image of its composite with the map to the final coalgebra.

\end{itemize}
